Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-04-25 paper.tex
some edits in Sect 2

\documentclass[a4paper,fleqn,usenatbib]{mnras}
\usepackage{txfonts}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx,color}	% Including figure files
%\usepackage{amsmath}	% Advanced maths commands
\usepackage{amssymb}	% Extra maths symbols
\usepackage{amsbsy}
\usepackage[normalem]{ulem}
\usepackage{mathrsfs,bm,xspace}
\newcommand{\bcdot}{\ensuremath{%
  \mathchoice%
   {\mskip\thinmuskip\lower0.2ex\hbox{\scalebox{1.5}{$\cdot$}}\mskip\thinmuskip}}%
   {\mskip\thinmuskip\lower0.2ex\hbox{\scalebox{1.5}{$\cdot$}}\mskip\thinmuskip}%        
   {\lower0.3ex\hbox{\scalebox{1.2}{$\cdot$}}}%  
   {\lower0.3ex\hbox{\scalebox{1.2}{$\cdot$}}}%
}

@@

\renewcommand{\vec}{\ensuremath{\mathbfit}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Vph}{V_\mathrm{ph}}
\newcommand{\mug}{\mu G}
\newcommand{\RH}{R_\rmn{RH}}
\newcommand{\bvel}{\ensuremath{\boldsymbol{\varv}}}
\newcommand{\bnabla}{\ensuremath{\boldsymbol{\nabla}}}
\newcommand\eb{\epsilon_\rmn{B}}

@@

\definecolor{mygreen}{rgb}{0.,0.5,0.}
\def\del#1{{}}
%\def\del#1{{\bf (DELETED TEXT)}}
\def\C#1{{\bf #1}}
\def\AP#1{{\bf  AP: #1}}
\def\APP#1{{\bf {\color{red} AP2: #1}}}
\def\SPO#1{{\bf {\color{blue} SPO: #1}}}
\def\CP#1{{\bf {\color{mygreen} CP: #1}}}

@@

[explain overall picture, $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$]

\subsection{Cosmic ray transport}
As previously noted, secondaries produced by shock accelerated CRp
have the wrong spatial profile to explain RH observations. Because
they arise from a two body process, they are too centrally
concentrated. They also produce $\gamma$-ray emission in excess of
Fermi-LAT upper limits
\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
if CRps stream in the ICM, then their spatial profile could
potentially flatten sufficiently \citep{ensslin11,wiener13}. This
scenario is very attractive: it generates seed electrons with the
right spatial footprint, and by removing CRps from the core, obeys
gamma-ray constraints. Turbulence plays two opposing roles:
Alfv{\'e}nic turbulence damps waves generated by the CR streaming
instability \citep{yan02,farmer04}, thus reducing self-confinement;
but compressible fast modes scatter CRs directly. Turbulent damping is
still efficient for highly subsonic conditions \citep{wiener13}, while
we assume compressible fast modes to only provide effective spatial
confinement during the periods of transonic, highly super-Alfv{\'e}nic
($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
stream out when the cluster is kinematically quiescent. Furthermore,
even Alfv{\'e}nic streaming timescales are relatively short
\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
which the CRp population is built up. Based on these findings, we
adopt a toy model for our \Mstream scenario in which CR streaming
instantaneously produces flat CRp profiles. \sout{We assume that CRs cannot
stream significantly past perpendicular $B$-fields at the accretion
shock, so that the total number of CRs is conserved within the galaxy
cluster during the streaming process.}

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|{{dp}\over{dt}}\right|_{\rm coul} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative (r) and Coulomb (coul) losses,
$D_{pp}$ is the momentum space diffusion coefficient, and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM. The $\bnabla\bcdot \bvel$ terms represent
adiabatic gains and losses.

@@

\subsection{Turbulent reacceleration}
We incorporate momentum diffusion for electrons and protons from
transit-time-damping (TTD) resonance with compressible MHD turbulence,
to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
TTD resonance requires the wave frequency
$\omega=k_\parallel\upsilon_\parallel$, where $k_\parallel$ and
$\upsilon_\parallel$ are the parallel (projected along the magnetic
field) wavenumber and particle velocity, respectively. This implies
that the particle transit time across the confining wave region
matches the wave period, $\lambda_{\parallel}/v_{\parallel}=T$. Note,
the CRs' gyroradius does not enter the resonance condition. Hence the
CRs that are in resonance with compressible waves experience Fermi-II
acceleration irrespectively of the length scale of the perturbation.

However, the resonance changes the component of particle momentum
parallel to seed magnetic fields, which over time leads to increasing
anisotropy in the particle distribution that decreases the efficiency
of reacceleration with time. As in \citet{brunetti11}, we assume that
there exists a mechanism---such as the firehose instability---that
isotropizes the CR distribution function at the gyroscale and on the
reacceleration time scale, which ensures sustained efficient
reacceleration with time. The particle pitch-angle averaged
momentum-diffusion coefficient of isotropic particles that couple to
fast magnetosonic modes via TTD resonance is \citep[][ Eqn. 47]{brunetti07}:
\begin{eqnarray}
  D_{pp}(p,t) = \frac{\pi}{16} \frac{p^2}{c\,\rho}
  \left\langle\frac{\beta |B_k|^2}{16 \pi \,W}\right\rangle
  I_\theta
  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
\label{eq:dpp}
\end{eqnarray}
where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
is the speed of light. The energy density $W$ of a mode in a
magnetized plasma stems from both electromagnetic fields and resonant
particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
beta-weighted magnetic-to-total energy density saturates to $\langle\beta
|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
\citealt{brunetti07}). The pitch angle of the CR momentum with the
magnetic field orientation is given by $\theta$, and
\begin{equation}
  \label{eq:I_theta}
  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
    |\cos \theta | }}
\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
\end{equation}
Here $V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves
given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
in \cite{brunetti07}, we initially assume that the velocity of
turbulent eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the
cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
Tab.~\ref{tab:timescales} for more details).

We focus on a scenario where the turbulence is injected at the largest
scale that is driven by the merging cluster and accreting matter. The
diffusion equation for isotropic MHD turbulence in $k$--space is given
by
\begin{eqnarray}
&{{\partial {\mathcal W}(k,t) }\over{\partial t}}
=
{{\partial}\over{\partial k}}
\left[
k^2 D_{kk}
{{\partial}\over{\partial k}}
\left( {{ {\mathcal W}(k,t) }\over{k^2}} \right)
\right]
- \sum_i \Gamma_i (k,t) {\mathcal W}(k,t)
+ I(k,t)\nonumber\\
&
\label{modes_kinetic}
\end{eqnarray}
where we assume that the volumetric injection rate of turbulence
$I(k,t)$ is constant over time with a fixed rate $I_0$ so that $I(k,t)
\equiv I(k) = I_0\,\delta (k - k_o)$. The different damping terms are
given by $\Gamma_i(k,t)$ and $D_{kk}$ is the wave--wave diffusion
coefficient of magnetosonic waves in the $k$--space represented by
\begin{equation}
  \label{eq:Dkk}
  D_{kk} \approx \Vph k^4
  \left(\frac{\mathcal{W}(k)}{\rho\,\Vph^2}\right)\,.
\end{equation}

We adopt a simplified isotropic MHD turbulent spectrum based on
Kraichnan's picture for the fast modes per elemental range $dk$ of the
form
\begin{equation}
  \label{eq:Wk}
  \mathcal{W}(k) =
\sqrt{2/7\,I_0\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
\end{equation}
for $k_0<k<k_\rmn{cut}$. Here we adopt a injection scale of the
turbulence, $k_0= 2\pi/(100~\mbox{kpc})$, that is in line with
previous work \citep{brunetti07,brunetti11} \AP{need to be motivated
  better? why not 1 Mpc}
%, motivated by recent state-of-art simulations \citep{2009A&A...504...33V,2011A&A...529A..17V,2015ApJ...800...60M}.
The profile of injected turbulence is also highly uncertain, however
we assume it correlates to the thermal energy density to some power of
the merging clusters. Hence we assume volumetric injection rate of
turbulent energy, $I_0\propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$,
and determine the normalization by requiring that the turbulent energy
in compressible modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k
\rmn{d}V = X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total
thermal energy. We adopt a turbulent energy ratio\footnote{Simulations
  show that the compressible modes contribute a factor $0.2-0.4$ to
  the total turbulent energy
  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
  total turbulent energy is typically $\sim15-70$\% of the thermal
  energy in a cluster \cite{2011A&A...529A..17V} which is in agreement
  with our adopted value of $X_\rmn{tu}$.}  $X_\rmn{tu}=0.2$ within
the radio halo. In this work we investigate different spatial models
for injected turbulence. With the above choice of normalization, the
turbulent energy density becomes $\epsilon_\rmn{turb} \propto
\epsilon_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
\Mprimary (see Figure~\ref{fig:turb} for visualization). Note that in
previous work on the Coma cluster, $\epsilon_\rmn{turb} \propto
\epsilon_\rmn{th}$ was adopted which roughly corresponds to
$\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
different distributions for seed CRes constitute the main differences
compared to our work. Our flatter turbulent profiles are motivated by
fits to cosmological simulations
\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
and the range indicates uncertainties of the turbulent profile in
Coma. Future observations (by Astro-H) and simulations will help to
clarify this issue. Provided dissipation of turbulence in the ICM is
collisionless, turbulent cascades of compressible modes become
suppressed when thermal and relativistic particles resonantly interact
with magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that
approaches the cascading timescale given by $\tau_{kk} \approx
k^2/D_{kk}$. Thus, the cascade is suppressed for wave numbers above
\begin{equation}
\label{eq:kc}
  k_\rmn{cut} \approx \frac{81}{14} \frac{I_0}{\rho \langle \Vph \rangle}
  \left(\frac{\langle\sum_i \Gamma_i(k,\theta)\rangle}{k}\right)^{-2}\,,
\end{equation}
where $2\pi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
effective mean free path for CRs, unless plasma instabilities can
mediate interactions between turbulence and particles on smaller
scales \citep{brunetti11}. In this work we only consider damping of
the turbulence via TTD due to thermal electrons, and neglect
subdominant damping with thermal protons and relativistic particles
(conversely, the turbulence has important effects on the
reacceleration of CRs). The latter will be subdominant in the ICM for
a CR-to-thermal energy density ratio $\lesssim 10 \%$
\citep{brunetti07}, which is always satisfied in our models. The
azimuthally averaged turbulent damping rate from thermal electrons
\citep{brunetti07} in a high-$\beta$ plasma is
\begin{equation}
\label{eq:Gamma_e}
\langle\Gamma_{\rmn{e}}\rangle \approx \langle k\,\Vph\,\sqrt{3\pi
  x/20}\exp(-5x/3)\sin^2{\theta}\rangle\approx 0.0435k\,\Vph, 
\end{equation}
where $x=(m_{\rmn{e}}/m_{\rmn{p}})/\cos^2{\theta}$. To compute the
synchrotron surface brightness profiles, we use the profile of the
magnetic field strengths derived from Faraday rotation observations of
Coma \citep{bonafede10} in combination with the density profile
derived from X-ray measurements \citep{1992A&A...259L..31B}.

@@

In principle, reacceleration via TTD leads to spectral steepening with
particle energy due to the inefficiency of the acceleration process to
counter the stronger cooling losses with increasing energy. Since
synchrotron emission peaks at frequency $\nu_\rmn{syn}\simeq 1\,
B/\mu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
spectral steepening of the radio spectrum (see
Fig.~\ref{fig:sync_spectrum}). A given radio window samples higher
energy electrons for a decreasing field strength in the cluster
outskirts. Hence, the spectral steepening with energy should translate
into a radial spectral steepening \citep{brunetti12}. However, because
of the weak dependence of the electron Lorentz factor on emission
frequency ($\gamma\propto\sqrt{\nu_\rmn{syn}}$), this effect is only
visible in our simulations for $\nu_\rmn{syn}\gtrsim5$~GHz. Most
importantly, our simulated fluid elements at a given radius sample a
broad distribution of shock history, density and temperature, which
implies very similar synchrotron brightness profiles at
$\nu_\rmn{syn}=352$~MHz and 1.4 GHz. The discrepancy of the observed
and simulated 1.4 GHz profiles could instead be due to systematic flux
calibration error in single dish observations. These could arise, for
instance, due to errors in point source subtraction. Interestingly, we
can match the 1.4 GHz data if we reduce the zero point by adding 10\%
of the central flux to every data point; this flattens the outer
profile\footnote{Lawrence Rudnick, private communication.}.
Alternatively, this may point to weaknesses in the theoretical
modeling of the particle acceleration process and may require a
stronger cutoff in the particle energy spectrum.

>>>>

\documentclass[fleqn,usenatbib,useAMS]{mnras}
\usepackage{amsmath}	% Advanced maths commands
\usepackage{txfonts}
\usepackage[T1]{fontenc}
\usepackage{ae,aecompl}
\usepackage{graphicx,color}	% Including figure files
\usepackage{amssymb}	% Extra maths symbols
\usepackage{amsbsy}
\usepackage[normalem]{ulem}
\usepackage{mathrsfs,bm,xspace}
\newcommand{\bcdot}{\ensuremath{%
  \mathchoice%
   {\mskip\thinmuskip\lower0.2ex\hbox{\scalebox{1.5}{$\cdot$}}\mskip\thinmuskip}}%
   {\mskip\thinmuskip\lower0.2ex\hbox{\scalebox{1.5}{$\cdot$}}\mskip\thinmuskip}%        
   {\lower0.3ex\hbox{\scalebox{1.2}{$\cdot$}}}%  
   {\lower0.3ex\hbox{\scalebox{1.2}{$\cdot$}}}%
}

@@

\renewcommand{\vec}{\ensuremath{\mathbfit}}
\newcommand{\dd}{\mathrm{d}}
\newcommand{\Vph}{V_\mathrm{ph}}
\newcommand{\mug}{\umu G}
\newcommand{\RH}{R_\rmn{RH}}
\newcommand{\bvel}{\ensuremath{\boldsymbol{\varv}}}
\newcommand{\bnabla}{\ensuremath{\boldsymbol{\nabla}}}
\newcommand\eb{\epsilon_\rmn{B}}
\newcommand{\dps}{\displaystyle}

@@

\definecolor{mygreen}{rgb}{0.,0.5,0.}
\def\del#1{{}}
%\def\del#1{{\bf (DELETED TEXT)}}
\def\C#1{{\bf #1}}
\def\AP#1{{\bf  AP: #1}}
\def\APP#1{{\bf {\color{blue} AP2: #1}}}
\def\SPO#1{{\bf {\color{red} SPO: #1}}}
\def\CP#1{{\bf {\color{mygreen} CP: #1}}}

@@

\SPO{explain overall picture, $\tau_\rmn{d}$ vs. $\tau_{\rmn{cl}}$}

\subsection{Cosmic ray transport}
As previously noted, secondaries produced by shock accelerated CRp
have the wrong spatial profile to explain RH observations. Because
they arise from a two body process, they are too centrally
concentrated. They also produce $\gamma$-ray emission in excess of
Fermi-LAT upper limits
\citep{2012ApJ...757..123A,brunetti12,2014ApJ...787...18A}. However,
if CRps stream in the ICM, then their spatial profile could
potentially flatten sufficiently \citep{ensslin11,wiener13}. This
scenario is very attractive: it generates seed electrons with the
right spatial footprint, and by removing CRps from the core, obeys
gamma-ray constraints. Turbulence plays two opposing roles:
Alfv{\'e}nic turbulence damps waves generated by the CR streaming
instability \citep{yan02,farmer04}, thus reducing self-confinement;
but compressible fast modes scatter CRs directly. Turbulent damping is
still efficient for highly subsonic conditions \citep{wiener13}, while
we assume compressible fast modes to only provide effective spatial
confinement during the periods of transonic, highly super-Alfv{\'e}nic
($M_{\rm A} \sim 5$) turbulence associated with mergers. Thus, CRs can
stream out when the cluster is kinematically quiescent. Furthermore,
even Alfv{\'e}nic streaming timescales are relatively short
\cite[$\sim 0.1-0.5$ Gyr;][]{wiener13} compared to the timescale on
which the CRp population is built up. Based on these findings, we
adopt a toy model for our \Mstream scenario in which CR streaming
instantaneously produces flat CRp profiles.

Given a seed population of CRs, we adopt essentially the same set of
plasma physics assumptions as the reacceleration model for RHs
\citep{brunetti07,brunetti11}. We solve the isotropic, gyro-phase
averaged Fokker-Planck equation (via a Crank-Nicholson scheme) for the
time evolution of the CRe distribution in the Lagrangian frame
\citep{brunetti07,brunetti11}:
\begin{eqnarray}
{{d f_{\rmn{e}}(p,t)}\over{d t}} &\!=&
\frac{\partial}{\partial p}
\left\{
f_{\rmn{e}}(p,t)\left[
\left|{{dp}\over{dt}}\right|_{\rm C} 
+ \frac{p}{3}\left(\bnabla\bcdot \bvel\right)
+ \left|{{dp}\over{dt}}\right|_{\rm r}\right.\right.
\nonumber\\
&-& \left.\left.{1\over{p^2}}{{\partial }\over{\partial p}}\left(p^2 D_{pp}\right) 
\right]\right\} - \left(\bnabla\bcdot \bvel\right) f_{\rmn{e}}(p,t)
\nonumber\\
&+& {{\partial^2 }\over{\partial p^2}}
\left[
D_{pp} f_{\rmn{e}}(p,t) \right]+ Q_{\rmn{e}}\left[p,t;f_{\rmn{p}}(p,t)\right]   \, .
\label{elettroni}
\end{eqnarray}
Here $f_{\rmn{e}}$ is the one-dimensional distribution in position $x$
(suppressed for clarity), momentum $p$ and time $t$ (which is
normalized such that the number density is given by
$n_{\rmn{e}}(t)=\int d p f_{\rmn{e}}(p,t)$), $d/dt=\partial/\partial
t+\bvel\bcdot\bnabla$ is the Lagrangian derivative, $\bvel$ is the gas
velocity, $|dp/dt|$ represents radiative (r) and Coulomb (C)
losses, $D_{pp}$ is the momentum space diffusion coefficient, and
$Q_{\rmn{e}}$ denotes the injection rate of primary and secondary
electrons in the ICM. The first term containing the expression
$\bnabla\bcdot \bvel$ represents Fermi-I acceleration and the second
term of this form describes adiabatic gains and losses.

@@

\subsection{Turbulent reacceleration}
We incorporate momentum diffusion for electrons and protons via the
transit-time-damping (TTD) resonance with compressible MHD turbulence,
to model Fermi-II reacceleration \citep{brunetti07,brunetti11}. The
TTD resonance requires the wave frequency to obey the resonance
condition, $\omega=k_\parallel\varv_\parallel$, where $k_\parallel$
and $\varv_\parallel$ are the parallel (projected along the magnetic
field) wavenumber and particle velocity, respectively. This implies
that the particle transit time across the confining wave region
matches the wave period,
$\lambda_{\parallel}/v_{\parallel}=\tau_{\rmn{wave}}$. Note, the CRs'
gyroradius does not enter the resonance condition. Hence the CRs that
are in resonance with compressible waves experience Fermi-II
acceleration irrespectively of the length scale of the perturbation.

However, the resonance changes the component of the particle momentum
parallel to the mean magnetic field, which over time leads to
increasing anisotropy in the particle distribution that decreases the
efficiency of reacceleration with time. As in \citet{brunetti11}, we
assume that there exists a mechanism---such as the firehose
instability---that isotropizes the CR distribution function at the
gyroscale and on the reacceleration time scale, which ensures
sustained efficient reacceleration with time.
\CP{add OoM}

The particle pitch-angle averaged momentum-diffusion coefficient of
isotropic particles that couple to fast magnetosonic modes via TTD
resonance is \citep[][ Eqn. 47]{brunetti07}:
\begin{eqnarray}
  D_{pp}(p,t) = \frac{\upi}{16} \frac{p^2}{\rho c}
  \left\langle\frac{\beta |B_k|^2}{16 \upi \,W}\right\rangle
  I_\theta
  \int_{k_\rmn{cut}}\mathcal{W}(k)k\,d k\,,
\label{eq:dpp}
\end{eqnarray}
where $\beta$ is the thermal-to-magnetic pressure ratio, and $c$
is the speed of light. The energy density $W$ of a mode in a
magnetized plasma stems from both electromagnetic fields and resonant
particles. For a high-$\beta$ plasma, the pitch angle averaged ratio of
beta-weighted magnetic-to-total energy density saturates to $\langle\beta
|B_k|^2/2W\rangle\approx 10^{1.4}$ (see Figure 2 in
\citealt{brunetti07}). The pitch angle of the CR momentum with the
magnetic field orientation is given by $\theta$, and
\begin{equation}
  \label{eq:I_theta}
  I_\theta=\int_0^{\arccos(\Vph/c)} d\theta {\frac{ \sin^3 \theta }{
    |\cos \theta | }}
\left[1+\left(\frac{\Vph}{c\,\cos{\theta}}\right)^2\right]^2.
\end{equation}
Here $V_\rmn{ph}$ is the phase velocity of the fast magnetosonic waves
given approximately by the sound speed, $\Vph \sim c_\rmn{s}$. For a
sound speed typical for the ICM of 1000~km/s, $I_\theta\approx5$. As
in \cite{brunetti07}, we initially assume that the velocity of
turbulent eddies is $V_0\approx 0.47 c_\rmn{s}$ throughout the
cluster. This gives a turbulent acceleration time scale, $\tau_{D} =
p^2/4D_{pp}$, that is typically few 100 Myrs in the ICM (see
Tab.~\ref{tab:timescales} for more details).

We focus on a scenario where the turbulence is injected at the largest
scale that is driven by the merging cluster and accreting matter. The
diffusion equation for isotropic MHD turbulence in $k$--space is given
by
\begin{equation}
  \begin{aligned}
\frac{\partial {\mathcal W}(k,t)}{\partial t}
=
\frac{\partial}{\partial k}
\left[
k^2 D_{kk}
\frac{\partial}{\partial k}
\left( \frac{{\mathcal W}(k,t)}{k^2} \right)
\right]
- \sum_i \Gamma_i (k,t) {\mathcal W}(k,t)
+ I(k,t)
\end{aligned}
\label{modes_kinetic}
\end{equation}
where we assume that the volumetric injection rate of turbulence
$I(k,t)$ is constant over time with a fixed rate $I_0$ so that $I(k,t)
\equiv I(k) = I_0\,\delta (k - k_o)$. The different damping terms are
given by $\Gamma_i(k,t)$ and $D_{kk}$ is the wave--wave diffusion
coefficient of magnetosonic waves in the $k$--space represented by
\begin{equation}
  \label{eq:Dkk}
  D_{kk} \approx \Vph k^4
  \left(\frac{\mathcal{W}(k)}{\rho\,\Vph^2}\right)\,.
\end{equation}

We adopt a simplified isotropic MHD turbulent spectrum based on
Kraichnan's picture for the fast modes per elemental range $dk$ of the
form
\begin{equation}
  \label{eq:Wk}
  \mathcal{W}(k) =
\sqrt{2/7\,I_0\,\rho\,\langle \Vph \rangle}\,k^{-3/2},
\end{equation}
for $k_0<k<k_\rmn{cut}$. Here we adopt an injection scale of the
turbulence, $k_0= 2\upi/\lambda_0$ with $\lambda_0 =100~\mbox{kpc}$,
that is in line with previous work \citep{brunetti07,brunetti11}. Note
that this length scale defines an eddy turn-over time
$\tau_{\rmn{eddy}}\sim2\upi\lambda_0/V_0\sim1.2$~Gyr with
$V_0=500\,\rmn{km~s}^{-1}$, characteristic of a merger event.

The profile of injected turbulence depends on the details of the
merger such as time during the merger, the impact parameter, the
merger mass ratio, and the degree of cluster anisotropy
\citep{2015ApJ...800...60M}. We parametrize these uncertainties and
assume that it scales with the thermal energy density to some
power. Hence we assume volumetric injection rate of turbulent energy,
$I_0\propto \epsilon_\rmn{th}^{\alpha_\rmn{tu}}$, and determine the
normalization by requiring that the turbulent energy in compressible
modes $E_\rmn{turb}=\int \int \mathcal{W}(k) \rmn{d}k \rmn{d}V =
X_\rmn{tu} E_\rmn{th}$, where $E_\rmn{th}$ is the total thermal
energy. We adopt a turbulent energy ratio $X_\rmn{tu}=0.2$ within the
radio halo.\footnote{Simulations show that the compressible modes
  contribute a factor $0.2-0.4$ to the total turbulent energy
  \citep{2013ApJ...771..131B,2015ApJ...800...60M}. Furthermore, the
  total turbulent energy, which can be decomposed into a slenoidal and
  compressible component, is typically $\sim15-70$\% of the thermal
  energy in a cluster \citep{2011A&A...529A..17V}; in agreement with
  our adopted value of $X_\rmn{tu}$.} In this work we investigate
different spatial models for injected turbulence. With the above
choice of normalization, the turbulent energy density becomes
$\epsilon_\rmn{turb} \propto
\epsilon_\rmn{th}^{(\alpha_\rmn{tu}+1)/2}/T^{1/4}$, where $T$ is the
temperature of the gas, $\alpha_\rmn{tu}= 0.67$ for \Mflatturb,
$\alpha_\rmn{tu}= 0.82$ for \Mstream, and $\alpha_\rmn{tu}= 0.88$ for
\Mprimary (see Figure~\ref{fig:turb} for visualization).

Note that in previous work on the Coma cluster, $\epsilon_\rmn{turb}
\propto \epsilon_\rmn{th}$ was adopted which roughly corresponds to
$\alpha_\rmn{tu}= 1$ \citep{brunetti12} and together with the
different distributions for seed CRes constitute the main differences
compared to our work. Our flatter turbulent profiles are motivated by
fits to cosmological simulations
\citep{2009ApJ...705.1129L,2010ApJ...725.1452S,2011A&A...529A..17V,2012ApJ...758...74B}
and the range indicates uncertainties of the turbulent profile in
Coma. Future observations (by Astro-H) and simulations will help to
clarify this issue. Provided dissipation of turbulence in the ICM is
collisionless, turbulent cascades of compressible modes become
suppressed when thermal and relativistic particles resonantly interact
with magnetosonic waves via TTD on a timescale $\Gamma^{-1}$ that
approaches the cascading timescale given by $\tau_{kk} \approx
k^2/D_{kk}$. Thus, the cascade is suppressed for wave numbers above
\begin{equation}
\label{eq:kc}
  k_\rmn{cut} \approx \frac{81}{14} \frac{I_0}{\rho \langle \Vph \rangle}
  \left(\frac{\langle\sum_i \Gamma_i(k,\theta)\rangle}{k}\right)^{-2}\,,
\end{equation}
where $2\upi/k_\rmn{cut}\sim 0.1-1$~kpc in the ICM. This constitutes an
effective mean free path for CRs, unless plasma instabilities can
mediate interactions between turbulence and particles on smaller
scales \citep{brunetti11}.

In this work we only consider damping of the turbulence via TTD due to
thermal electrons, and neglect subdominant damping with thermal
protons and relativistic particles (conversely, the turbulence has
important effects on the reacceleration of CRs). The latter will be
subdominant in the ICM for a CR-to-thermal energy density ratio
$\lesssim 10 \%$ \citep{brunetti07}, which is always satisfied in our
models. The azimuthally averaged turbulent damping rate from thermal
electrons \citep{brunetti07} in a high-$\beta$ plasma is
\begin{equation}
\label{eq:Gamma_e}
\langle\Gamma_{\rmn{e}}\rangle \approx \langle k\,\Vph\,\sqrt{3\upi
  x/20}\exp(-5x/3)\sin^2{\theta}\rangle\approx 0.0435k\,\Vph, 
\end{equation}
where $x=(m_{\rmn{e}}/m_{\rmn{p}})/\cos^2{\theta}$. To compute the
synchrotron surface brightness profiles, we use the profile of the
magnetic field strengths derived from Faraday rotation observations of
Coma \citep{bonafede10} in combination with the density profile
derived from X-ray measurements \citep{1992A&A...259L..31B}.

@@

In principle, reacceleration via TTD leads to spectral steepening with
particle energy due to the inefficiency of the acceleration process to
counter the stronger cooling losses with increasing energy. Since
synchrotron emission peaks at frequency $\nu_\rmn{syn}\simeq 1\,
B/\umu\rmn{G} (\gamma/10^4)^2\,\rmn{GHz}$, this translates into a
spectral steepening of the radio spectrum (see
Fig.~\ref{fig:sync_spectrum}). A given radio window samples higher
energy electrons for a decreasing field strength in the cluster
outskirts. Hence, the spectral steepening with energy should translate
into a radial spectral steepening \citep{brunetti12}. However, because
of the weak dependence of the electron Lorentz factor on emission
frequency ($\gamma\propto\sqrt{\nu_\rmn{syn}}$), this effect is only
visible in our simulations for $\nu_\rmn{syn}\gtrsim5$~GHz. Most
importantly, our simulated fluid elements at a given radius sample a
broad distribution of shock history, density and temperature, which
implies very similar synchrotron brightness profiles at
$\nu_\rmn{syn}=352$~MHz and 1.4 GHz. The discrepancy of the observed
and simulated 1.4 GHz profiles could instead be due to systematic flux
calibration error in single dish observations. These could arise, for
instance, due to errors in point source subtraction. Interestingly, we
can match the 1.4 GHz data if we reduce the zero point by adding 10\%
of the central flux to every data point; this flattens the outer
profile\footnote{Lawrence Rudnick, private communication.}.
Alternatively, this may point to weaknesses in the theoretical
modeling of the particle acceleration process and may require a
stronger cutoff in the particle energy spectrum.
